---
title: "Intro-tidy"
format: revealjs
engine: knitr
execute: 
  freeze: auto
---

```{r include=FALSE}
library(ggplot2)
library(dplyr)
```


# tidyverse {background-color="aquamarine"}

> The [tidyverse](https://www.tidyverse.org) is an opinionated collection of R packages designed for data science. All packages share an underlying design philosophy, grammar, and data structures.

## Why should we care about the tidyverse?

> What's the mean of `mpg` (miles per gallon) and the number of observations by `cyl` (cylinders) in the `mtcars` dataset?

::: columns

::: {.column width="50%"}
#### tidyverse
```{r}
#| echo: true
mtcars %>%
  group_by(cyl) %>%
  summarise(mean = mean(mpg), n = n())
```
:::

::: {.column width="50%"}
#### base R
```{r}
#| echo: true
mtcars_by <- by(mtcars, mtcars$cyl, function(df) {
  with(df, data.frame(
    cyl = cyl[[1]],
    mean = mean(mpg),
    n = nrow(df)
  ))
})
do.call(rbind, mtcars_by)
```
:::

:::

::: aside
Adapted from [dplyr base R](https://dplyr.tidyverse.org/articles/base.html#summarise-reduce-multiple-values-down-to-a-single-value)
:::